result_review.rmd

### 2015-11-20 finalwriteup/draft.rmd
final update

* A gap in machine learning predictive models which cater for variables with large amounts of missing data. the nature of consulting jobs is quite complex and historically, not all information about a project is possible to obtain. Variables with missing data are alternatively treated as optional bonus variables in a multi step model as opposed to missing information which must be imputed or deletion of the entire case that contains missing information.

@@

This chapter provides an overview of the literature available about current business to business (B2B) cost estimation methods, use cases of CRM data, as well as machine learning algorithms and statistical business prediction models. In particular, the literature on B2B decision strategy is centred around setting fixed consulting fees and methods of managing effective consulting projects. The most prominent statistical and machine-learning models developed for business applications shall be reviewed along with models applied to the most closely related business cases to this project.

@@

### 2.1.1 Contract Structures

* research into contract structures to prevent loss
* benefits of flexible type contracts
* Gap: mobilising when to implement flexible contracts - takes away from client relationship but jobs that make losses are pointless and eventually deteoriate relationships

@@

>>>>

* A gap in machine learning predictive models which cater for variables with large amounts of missing data. the nature of consulting jobs is quite complex and historically, not all information about a project is possible to obtain. Variables with missing data are alternatively treated as optional bonus variables in a multi-step model as opposed to missing information which must be imputed or deletion of the entire case that contains missing information.

@@

This chapter provides an overview of the literature available about current business to business (B2B) cost estimation methods, use cases of CRM data, as well as machine learning algorithms and statistical business prediction models. The most prominent statistical and machine-learning models developed for business applications shall be reviewed along with models applied to the most closely related business cases to this project. Gaps in past research will also be highlighted.

@@

* Previous methods to address problem of cost estimation

    *

@@

**

### 2015-11-20 financial.rmd
final update

profit.cv<- function(df.string = "all10mice", method = "log", seed = 300, k.folds = 8){

@@

                        #pROC
                        pred.p <- roc(test$f.rpdol, pred)

>>>>

profit.cv<- function(df.string = "all10mice", method = "boost", seed = 300, k.folds = 3){

@@

                        #pROC
                        pred.p <- roc(test$f.rpdol, pred)
                        # plot.roc(pred.p, col= colours[i], print.thres=T)

### 2015-11-20 prob_review.rmd
final update

---
title: "Financial_Analysis"
author: "Amy Cook"
date: "October 21, 2015"
output: word_document
---

#Assess financial implications for a predictive model

We typically get a confusion matrix built from probabilities

@@

```{r, echo=FALSE}
test.pred <- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/test_review.csv')
all7d <- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7d.csv')
test.pred<- merge(test.pred, all7d %>% select(mlsto, balance.mlsto), by = "mlsto")

@@

Create vector of profit points

threshold<- seq(0,1, by=.05)
fin.prof<- rep(0, length(threshold))

for(i in 1:length(threshold)){
        prof<- data.frame("balance" = test.pred$balance.mlsto, 
                  "pred" = test.pred$pred,
                  "ans" = test.pred$b.rpdol)
        #pred = probabilities
        prof$conf <- rep(0, nrow(prof))
        prof$conf <- ifelse(prof$pred >= threshold[i] & prof$ans == 1, 'TP', prof$conf)
        prof$conf <- ifelse(prof$pred >= threshold[i] & prof$ans == 0, 'FP', prof$conf)
        prof$profit<- rep(0, nrow(prof))
        prof$profit<- ifelse(prof$conf %in% "TP", -prof$balance, prof$profit)
        prof$profit<- ifelse(prof$conf %in% "FP", -prof$balance, prof$profit)

        fin.prof[i] = sum(prof$profit)

prof.plot<- data.frame("threshold" = threshold, "final.profit" = fin.prof)

ggplot(prof.plot, aes(x=threshold, y=final.profit)) + geom_point() + geom_line()

# if say no to all jobs with higher than prob of 0.5, save $500,000

head(prof)

####
# SUMMARY STATS
####

# would dismiss 56 jobs
prof %>% filter(pred>=0.5) %>% nrow

# would dismiss 19 profitable jobs
prof %>% filter(pred >= 0.5 & balance > 0) %>% nrow
#out of 607
prof %>% filter(balance > 0) %>% nrow

# would dismiss 37 losing jobs
prof %>% filter(pred >= 0.5 & balance < 0) %>% nrow
#out of 135
prof %>% filter(balance < 0) %>% nrow

#without algorithm, balance would be $1,475,642
orig.bal<- sum(prof$balance)

# without any losing jobs, balance would be $2,516,246
orig.prof<- prof %>% filter(balance > 0) %>% sum

# without any profitable jobs, balance would be -$1,040,322
orig.loss<- prof %>% filter(balance < 0) %>% sum

#how much real profit would you be dismissing? $82631
prof.dismis<- prof %>% filter(pred >= 0.5 & balance > 0) %>% select(balance) %>% sum
#how much real loss would you be avoiding? $566,481.6
loss.dismis<- prof %>% filter(pred >= 0.5 & balance < 0) %>% select(balance) %>% sum
# total benefit = $483,850
algor.prof<- -(loss.dismis + prof.dismis)

# total balance would be $1,959,492
sum(prof$balance) + algor.prof

# a 32.8% improvement
algor.prof/sum(prof$balance)

@@

profit.cv<- function(df.string = "all10mice", method = "boost", seed = 300, k.folds = 3){

        results = data.frame('orig.bal' = rep(0, k.folds), 'orig.prof' = rep(0, k.folds), 
                             'orig.loss' = rep(0, k.folds),
                             'prof.dismis' = rep(0, k.folds), 'loss.dismis' = rep(0, k.folds), 
                             'algor.prof' = rep(0, k.folds),
                             'improv' = rep(0, k.folds), 'thresh' = rep(0, k.folds),
                             'auc' = rep(0, k.folds))
        colours <- c("red", "yellow", "green", "blue", "purple")

@@

                        results$auc[j] <- auc(pred.p)

@@

                        #create vector of profit points

                        threshold = seq(0,1, by = .05)
                        fin.prof = rep(0, length(threshold))

                        for (i in 1:length(threshold)) {
                                prof <- data.frame("balance" = test.pred$balance.mlsto,
                                "pred" = test.pred$pred,
                                "ans" = test.pred$b.rpdol)

                                #pred = probabilities
                                prof$conf <- rep(0, nrow(prof))
                                prof$conf <- ifelse(prof$pred >= threshold[i] & prof$ans == 1, 'TP', prof$conf)
                                prof$conf <- ifelse(prof$pred >= threshold[i] & prof$ans == 0, 'FP', prof$conf)
                                prof$profit <- rep(0, nrow(prof))
                                prof$profit <- ifelse(prof$conf %in% "TP",-prof$balance, prof$profit)
                                prof$profit <- ifelse(prof$conf %in% "FP",-prof$balance, prof$profit)

                                fin.prof[i] = sum(prof$profit)

                        prof.plot<- data.frame("threshold" = threshold, "final.profit" = fin.prof)

                        print(
                        ggplot(prof.plot, aes(x=threshold, y=final.profit)) + geom_point() + geom_line()
                        )

                        best.thresh = arrange(prof.plot, -final.profit)[1,1]
                        results$thresh[j] = best.thresh

                        ####
                        # SUMMARY STATS
                        ####

                        #without algorithm, balance would be $1,475,642
                        results$orig.bal[j] = sum(prof$balance)
                        # without any losing jobs, balance would be $2,516,246
                        results$orig.prof[j] = prof %>% filter(balance > 0) %>% sum
                        # without any profitable jobs, balance would be -$1,040,322
                        results$orig.loss[j] = prof %>% filter(balance < 0) %>% sum
                        #how much real profit would you be dismissing? $82631
                        temp<- prof %>% filter(pred >= best.thresh & balance > 0)
                        results$prof.dismis[j] = ifelse(nrow(temp)>0, temp %>% select(balance) %>% sum,
                                                        0)
                        #how much real loss would you be avoiding? $566,481.6
                        results$loss.dismis[j] = prof %>% filter(pred >= best.thresh & balance < 0) %>% 
                                select(balance) %>% sum

@@

        # total benefit = $483,850
        results = transform(results, algor.prof = -(loss.dismis + prof.dismis))
        results = transform(results, improv = algor.prof/orig.bal)

        return(results)

@@

results.1 <- profit.cv(df.string = "all10mice", method = "log", seed = 400, k.folds = 8)
results.2 <- profit.cv(df.string = "all10mice", method = "boost", seed = 400, k.folds = 8)
results.3 <- profit.cv(df.string = "all10mice", method = "rf", seed = 300, k.folds = 3)

>>>>

---
title: "result_review.rmd"
author: "Amy Cook"
date: "November 19, 2015"
output: word_document
---

@@

all7d <- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7d.csv')

@@

Assemble full data set with predictions

@@

predict.all<- function(df.string = "all10mice", method = "boost", seed = 300, k.folds = 3){

        #create dataset for final results to tag onto
        all10full = NULL

@@

                        auc(pred.p)

@@

                        all10full <- rbind(all10full, test.pred)

@@

        return(all10full)

@@

results.1 <- predict.all(df.string = "all10mice", method = "boost", seed = 400, k.folds = 8)
